A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-02-19 papers/execution-model/model.tex
Add files via upload
revised sec-3 and sec-6

The main issues in using a blockchain oracle are trust and security \cite{trustworthy}. The researchers in \cite{reliable-oracle} have proposed a decentralized oracle to verify the interactions and solve the disputes between blockchain smart contracts and oracles. Similarly, researchers in \cite{reliablity-oracles} focus on the notion of trust and provide a framework to perform reliability analysis of various blockchain oracle platforms. Closely following our work, in \cite{interact-coq} the authors present a model-executable specification of smart-contract execution in Coq. Their formalizations target Ethereum and Tezos.

>>>>

The main problems with using a blockchain oracle are the untrusted data provided maliciously or inaccurately \cite{trustworthy}. The researchers in \cite{reliable-oracle} propose an oracle equipped with verification and disputation mechanisms. Similarly, researchers in \cite{reliablity-oracles} provide a framework for performing reliability analysis of various blockchain oracle platforms. Closely following our work, the authors in \cite{interact-coq} present a model-executable specification of smart-contract execution in Coq. Their formalizations target Ethereum and Tezos.
